\chapter{Requirements}
Bellow is given the the requirements for the system. Definitions for the requirements:
\begin{itemize}
    \item The user or users er the actors interacting with the Password Manager. (Customers)
    \item The database maintainer is the actors owning and maintaining the database and password manager. (Owners)
    \item In \ref{bul:req:inactive} the system is the user's system, on which the password manager client is running.
    \item Two users cannot have the same password.
\end{itemize}

\section{General}
\newcounter{tempCounter} % Used to store number of reqs.
\begin{enumerate}[label={\textbf{Req. \arabic*}}, ref={req. \arabic*}]
    % General
    \item The Password Manager should be able to have multiple users.
    \item Each User should have a password database.
    \item Each password in the password database should hold the login information for an account, and some match information to where that account is used.

\end{enumerate}
\section{Access}
\begin{enumerate}[resume*]

    \item For the user to be able to login the user must provide a correct password to the given username.
    \item A device should be authorized for each user before the user can login through that device.
    \item If the user has been inactive on the system for 5 minutes while logged in on the Password Manager, the system should log the user out. \label{bul:req:inactive}

\end{enumerate}
\section{Security}
\begin{enumerate}[resume*]

    \item Encryption:
          \begin{enumerate}[label={\textbf{\arabic*.}}]
              \item The user's password database should be encrypted while the user is logged out.
              \item The user's password database should be decrypted while the user is logged in.
          \end{enumerate}
    \item Only the logged in user should be able to access their database unencrypted. The database maintainer should not be able to decrypt it from the backend.
    \item Each user's encryption key should be unique.

\end{enumerate}